Manuscript

### 2019-01-11 manuscript.Rmd
work on manuscript, mut results, venn diagrams

floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(papaja)
library(bookdown)
library(VennDiagram)
# install.packages("tinytex")
# tinytex::install_tinytex()
# install.packages("citr")
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
# update wordcount in Addins
```

@@

```{r functions, echo=FALSE, include=FALSE}
e2exp_converter <- function(string, p_type) {
  e <- formatC(as.numeric(string), format = "e", digits = 1)
  if(p_type == "pk") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  if(p_type == "p") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  if(p_type == "padj") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  return(exp)
}
```

@@

# CCLE: GE/CN correlations
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"

@@

**Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P**

Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all pairwise combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*). At an unadjusted $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.

Controlling for a false discovery rate (FDR) < 5%, selumetinib-*BRAF* (`r e2exp_converter(ccle_signif_g2p_grid[ccle_signif_g2p_grid$Drug_Gene == "selumetinib_BRAF",]$p.adj, p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`). CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*. There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`), Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)).

```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")

ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)

drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
# in GDSC only
drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
# in GDSC and CTRP only
drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
# in CTRP only
drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
# in CTRP and CCLE only
drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)

grid.newpage()
grid.draw(drug_venn)
```

We observe little concordance between the number of interpretations for each G2P association and the significance of mutation status on AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets. This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.

We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...

**Cut this analysis since we are comparing distributions of p-values?**

@@

In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: `r paste(g2p_lins[1:length(g2p_lins) -1], collapse = ", ")`, and `r g2p_lins[length(g2p_lins)]`. CCLE had data for `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin))` DGLs, CTRP had data for `r length(unique(ctrp_data_g2p_dgl$Drug_Gene_Lin))`, and GDSC had data for `r length(unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))`, yielding a total of `r length(union(union(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` unique DGLs across all three datasets. Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets,

@@

@@

```{r crispr-venn, echo = FALSE}
crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)

# in GE only
crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
# in CN only
crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
# intesection
crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")

grid.newpage()
grid.draw(crispr_venn)
```

@@

Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018]. `compare_means` does Benjamini-Hochberg p-value adjustment using the `p,adjust` function from the `stats` base R package.

For computing Spearman correlation coefficients. If there were 3 or fewer data points, then the correlation was not done and a value of NA was supplied.

>>>>

floatsintext      : yes
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(papaja)
library(bookdown)
library(VennDiagram)
library(lettercase)
# install.packages("tinytex")
# tinytex::install_tinytex()
# install.packages("citr")
# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
# update wordcount in Addins
```

@@

```{r functions, echo=FALSE, include=FALSE}
e2exp_converter <- function(string, p_type) {
  # Convert p-vals in scientific format to latex-equation style p-vals with exponent
  e <- formatC(as.numeric(string), format = "e", digits = 1)
  if(p_type == "pk") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  if(p_type == "p") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  if(p_type == "padj") {
    if(grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-(\\d+)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
    }
    if(!grepl("(\\d+)e-([1-9]+)", e)) {
      exp <- sub("(.+)e-0(\\d)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
    }
  }
  return(exp)
}

dg2intext_converter <- function(drug_gene) {
  # Convert drug-gene strings to have italic gene name
  d_g <- strsplit(drug_gene, split = "_")
  dg <- paste0(d_g[[1]][1], "-*", d_g[[1]][2], "*")
  return(dg)
}
```

@@

# Mut summaries
drug_grid_shared_dg <- union(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene, union(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene, gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene))

# CCLE: GE/CN correlations
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(
  Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
  Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
  Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
  Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
  Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
  Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
  Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
  Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"

@@

Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P associations tested in the CCLE, CTRP, and GDSC drug screens. Of the `r length(g2p_druggenes)` G2P associations, data was available for `r length(ccle_signif_g2p$Drug_Gene)` associations in CCLE, `r length(ctrp_signif_g2p$Drug_Gene)` in CTRP, and `r length(gdsc_signif_g2p$Drug_Gene)` in GDSC. Controlling for a false discovery rate (FDR) < 5%, CCLE yielded no significant correlations (Wilcoxon rank-sum tests, `r ccle_signif_g2p_exp`), though the most significant G2P association was `r dg2intext_converter(ccle_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p$p.adj[1], p_type = "padj")`). In CTRP, AUC from `r nrow(filter(ctrp_signif_g2p[!is.na(ctrp_signif_g2p$p.signif.adj),]))` drug-gene associations correlated with the gene's mutation status (`r ctrp_signif_g2p_exp`): `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[1], p_type = "padj")`), `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[2], p_type = "padj")`), and `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[3])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[3], p_type = "padj")`). `r str_ucfirst(dg2intext_converter(gdsc_signif_g2p$Drug_Gene[1]))` (`r e2exp_converter(gdsc_signif_g2p$p.adj[1], p_type = "padj")`) and `r dg2intext_converter(gdsc_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(gdsc_signif_g2p$p.adj[2], p_type = "padj")`) were significant in GDSC (`r gdsc_signif_g2p_exp`).

> **(???) Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P?**

To test for potentially novel drug-gene associations, we conducted similar Wilcoxon rank-sum tests for all pairwise combinations of G2P genes and drugs tested in the three drug screens (*Figures 1B and 2A*). At an unadjusted $\alpha = 0.05$, the tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.

Controlling for a FDR < 5%, `r dg2intext_converter(ccle_signif_g2p_grid$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p_grid$p.adj[1], p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`). CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*. There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`). Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)). Of the `r length(drug_grid_shared_dg)` significant drug-gene associations across datasets, `r length(intersect(drug_grid_shared_dg, g2p_druggenes))` were G2P associations. The remaining `r length(drug_grid_shared_dg) - length(intersect(drug_grid_shared_dg, g2p_druggenes))` associations were `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[1])`, `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[2])`, and `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[3])`.

> **(???) Trametinib and selumetinib are both *MEK* inhibitors, and pazopanib is a *VEGFR* inhibitor. VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival. This pathway includes *RAS*, *BRAF*, and *MEK* proteins. These results underscore the importance of the MAPK/ERK signaling pathway in cancer.**

However, taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets. This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response. We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...

```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("./plots/manuscript/drugscreen_venn.png")
```

> **(???) Cut this analysis since we are comparing distributions of p-values?**

@@

In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: `r paste(g2p_lins[1:length(g2p_lins) -1], collapse = ", ")`, and `r g2p_lins[length(g2p_lins)]`. CCLE had data for `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin))` DGLs, CTRP had data for `r length(unique(ctrp_data_g2p_dgl$Drug_Gene_Lin))`, and GDSC had data for `r length(unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))`, yielding a total of `r length(union(union(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` unique DGLs across all three datasets. Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets.

@@

> **(???) KS test results**

(Figure\ \@ref(fig:ksplot))

```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap="Comparison of Spearman correlation coefficients derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations. Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not. Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests."}
knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.png")
```

@@

```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("./plots/manuscript/crispr_venn.png")
```

@@

Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018]. `compare_means` does Benjamini-Hochberg p-value adjustment using the `p.adjust` function from the `stats` base R package.

For computing Spearman correlation coefficients, we used the `cor.test` base R package. If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.

### 2019-01-11 manuscript_analysis.Rmd
work on manuscript, mut results, venn diagrams

@@

@@

ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
g2p_corr_stats

@@

Plot of Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages:
```{r fig.height=6, fig.width=12}
g2p_corr_4plot <- g2p_corr_all
g2p_corr_4plot$p <- NULL
g2p_corr_4plot$Mut_Signif <- NULL
g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)

@@

>>>>

Venn diagram between GE and CN:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)

# in GE only
crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
# in CN only
crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
# intesection
crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")

png("./plots/manuscript/crispr_venn.png")
grid.newpage()
grid.draw(crispr_venn)
dev.off()
```

@@

Venn diagram of drug-gene associations:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")

ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)

drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
# in GDSC only
drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
# in GDSC and CTRP only
drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
# in CTRP only
drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
# in CTRP and CCLE only
drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)

png("./plots/manuscript/drugscreen_venn.png")
grid.newpage()
grid.draw(drug_venn)
dev.off()
```

@@

ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
g2p_corr_stats$Metric <- ifelse(g2p_corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
g2p_corr_stats

@@

Plot of Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages:
```{r fig.height=6, fig.width=12}
g2p_corr_4plot <- g2p_corr_all
g2p_corr_4plot$p <- NULL
g2p_corr_4plot$Mut_Signif <- NULL
g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")

@@

```{r fig.height=6, fig.width=12}
g2p_ks_res_plot_spearman <- ggplot(data = filter(g2p_corr_4plot, Correlation_Method == "Spearman")) +
  facet_grid(Metric ~ Dataset, labeller = labeller(yfacet = c('CN' = "Copy Number", 'GE' = "Gene Expression"))) +
  geom_violin(aes(y = Correlation, x = G2P_DGL, fill = Dataset, color = Dataset, alpha = G2P_DGL)) +
  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
  geom_jitter(width = 0.3, alpha = 0.8, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
  theme(legend.position = "none") +
  scale_alpha_manual(values = c("Yes" = 0.6, "No" = 0.2)) +
  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4", "CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  coord_cartesian(ylim = c(-1, 1)) +
  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"), aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
  labs(x = "Is the lineage in a G2P DGL?", y = "Spearman Correlation Coefficient")
g2p_ks_res_plot_spearman

# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 450, width = 12, height = 6, units = "in")
```
